\documentclass[margin,line,11pt]{res}
\usepackage{times}
\oddsidemargin -.48in
\evensidemargin -.5in
\topmargin -.35in
\textwidth=6in
\textheight=10in
\itemsep=0in
\parsep=0in


\begin{document}

\name{\huge \sc Annie Sauer Booth \vspace*{.1in}}

\begin{resume}


\vspace{-0.1cm}
\section{\bf CONTACT\\INFO}
\vspace{.05in}
\begin{tabular}{@{}p{2.7in}rp{2in}}
Department of Statistics  & {\it E-mail:} & annie\_booth@vt.edu \\            
Virginia Tech & {\it Homepage:} & www.anniesbooth.com \\   
Hutcheson Hall, 250 Drillfield Drive \\     
Blacksburg, VA 24061, USA  
\end{tabular}

\medskip
\section{\bf RESEARCH INTERESTS}

Bayesian statistics, surrogate modeling, statistical computing, design of experiments, 
uncertainty quantification, optimization, calibration, reliability.  
With applications to computer experiments.

\medskip
\section{\bf EDUCATION}

{\sc Virginia Polytechnic Institute and State University} \\
{\bf Ph.D.} Statistics, May 2023, advised by Robert B.~Gramacy \& David Higdon \\
Dissertation: {\it Deep Gaussian Process Surrogates for Computer Experiments} \\
{\bf M.S.} Statistics, December 2019 

{\sc Auburn University} \\
Honors Scholar; 4.00 GPA \\
{\bf B.S.} Applied Mathematics, May 2018 \\
{\bf B.A.} Psychology, May 2018

\medskip
\section{\bf PROFESSIONAL \\ POSITIONS}

{\bf Assistant Professor}, Department of Statistics, {\sc Virginia Tech} \hfill 2025 - Present \\
{\bf Assistant Professor}, Department of Statistics, {\sc NC State University} \hfill 2023 - 2024

\bigskip
\section{\bf HONORS \& AWARDS}

ISBA Savage Award Finalist; 2023 \\
Shewell Award for presentation at Fall Technical Conference; 2023 \\
Mary G. and Joseph Natrella Scholarship; 2022 \\
ASA Physical and Engineering Sciences Section Student Paper Competition Winner; 2022 \\
ISBA Best Student/Postdoc Contributed Paper Award; 2021 \\
ISBA Industrial Statistics Student Presentation Award, Honorable Mention; 2021 \\
Virgina Tech Myers Award for excellence in linear models and design of experiments; 2019 \\
Virginia Tech Boyd Harshbarger Award for excellence as a first-year graduate student; 2019 \\
Virginia Tech Jean D. Gibbons Fellowship; 2018 \\
Auburn University Dean's Medal in Mathematics; 2018 \\
Auburn University Dean's Award for Academic Excellence; 2018

\medskip
\section{\bf{IN REVIEW}}

Walsh, S. A., {\bf Booth, A. S.}, Higdon, D., Clark, J., Moran, K. R., \& Heitmann, K. (2025). Bayesian deep Gaussian processes for correlated functional data: A case study in cosmological matter power spectra.  arXiv:2507.18683

Cooper, A., {\bf Booth, A. S.}, \& Gramacy, R. B. (2025). Modernizing full posterior inference for surrogate modeling of categorical-output simulation experiments. arXiv:2501.14946

{\bf Booth, A. S.} \& Renganathan, S. A. (2025). Two-stage design for failure probability estimation with Gaussian process surrogates. arXiv:2410.04496

Wycoff, N., Smith, J. W., {\bf Booth, A. S.}, \& Gramacy, R. B. (2024). Voronoi candidates 
for Bayesian optimization. arXiv:2402.04922

\pagebreak
\section{}
\hfill {\bf Curriculum Vitae:} Annie S. Booth \  --- \  2
\medskip

Moran, K. R., Payne, R., Lawrence, E., Higdon, D., Walsh, S. A., {\bf Booth, A. S.}, Kwan, J., Day, A., Habib S. \& Heitmann, K. (2024). Bayesian deep process convolutions: An application in cosmology. arXiv:2411.14747

\section{\bf{PEER- \\ REVIEWED \\ PAPERS}}

Barnett, S., Beesley, L. J., {\bf Booth, A. S.}, Gramacy, R. B., \& Osthus, D. (2024). Monotonic 
warpings for additive and deep Gaussian processes. {\it Statistics and Computing, to appear}. arXiv:2408.01540

{\bf Booth, A. S.}, Renganathan, S. A., \& Gramacy, R. B. (2025). Contour location
for reliability in airfoil simulation experiments using deep Gaussian
processes.  {\it Annals of Applied Statistics, 19}(1), 191-211. arXiv:2308.04420

{\bf Sauer, A.}, Cooper, A., \& Gramacy, R. B. (2023). Vecchia-approximated
deep Gaussian processes for computer experiments. {\it Journal of Computational
and Graphical Statistics, 32}(3), 824-837. arXiv:2204.02904

Gramacy, R. B., {\bf Sauer, A.}, \& Wycoff, N. (2022). Triangulation 
candidates for Bayesian optimization. {\it Advances in Neural Information
Processing Systems (NeurIPS), 35,} 35933-35945. arXiv:2112.07457

{\bf Sauer, A.}, Gramacy, R. B., \& Higdon, D. (2021). Active learning 
for deep Gaussian process surrogates. {\it Technometrics, 65}(1), 4-18. 
arXiv:2012.08015

\section{OTHER \\ PUBLICATIONS}

{\bf Booth, A. S.}, Gramacy, R. B., \& Renganathan A. (2024). Actively learning deep Gaussian
process models for failure contour and reliability estimation.  In {\it AIAA Scitech 2024 Forum} (p.0577).

{\bf Booth, A. S.}, Cooper, A., \& Gramacy, R. B. (2024). Nonstationary
Gaussian process surrogates. {\it Handbook of Uncertainty Quantification, to appear}; arXiv:2305.19242

{\bf Sauer, A.} (2022). {\tt deepgp}: an {\sf R}-package for Bayesian deep Gaussian 
processes.  {\it ISBA Bulletin}, Software Highlight; December, 29(4).

{\bf Sauer, A.} \& Gramacy R. B. (2022). Discussion of paper by Marmin \& Filippone.  An
invited discussion of ``Deep Gaussian processes for calibration of computer models''
by S. Marmin \& M. Filippone. {\it Bayesian Analysis}, pp. 1-30.

Stanford, B., {\bf Sauer, A.}, Jacobson, K., \& Warner, J. (2022). 
Gradient-enhanced reliability analysis of transonic aeroelastic 
flutter. In {\it AIAA Scitech 2022 Forum} (p. 0632).

\medskip
\section{\bf THESIS}

Ph.D. Thesis, Department of Statistics.  {\it Deep Gaussian Process
Surrogates for Computer Experiments} (2023). Virginia Polytechnic Institute
and State University; {\it http://hdl.handle.net/10919/114845}

\medskip
\section{\bf OPEN SOURCE SOFTWARE}

{\tt deepgp}: An {\sf R}--package for deep Gaussian processes 
using fully-Bayesian MCMC.\\
{\sl https://CRAN.R-project.org/package=deepgp}

{\tt runexp}: An {\sf R}--package for softball run expectancy using 
discrete Markov chains and Monte Carlo simulation; with S.~Merkes.
{\sl https://CRAN.R-project.org/package=runexp}

\pagebreak
\section{}
\hfill {\bf Curriculum Vitae:} Annie S. Booth \  --- \  3
\medskip

\section{\bf GRANTS}

Lawrence Livermore National Laboratory, Academic Collaboration Team: Dimension reduction with 
deep Gaussian process models [PI] Awarded in December 2024 for 3 years, with Kevin Quinlan
and Laura Wendelberger. \hfill \$258,446

National Science Foundation (NSF), Collaborative Research: MATH-DT: {\it Gradient-enhanced
deep Gaussian processes for optimization of diffusive high-speed unsteady mixers} [PI]
Awarded in August 2024 for 3 years, with James Braun.  \hfill \$498,290

NCSU Controlled Environment Agriculture Consortium: {\it Computational fluid dynamics for
enhanced understanding of air movement, sensor placement, and plant arrangement in controlled
environment agriculture} [PI] Awarded in June 2024 for 1 year, with James Braun and 
Ricardo Hernandez. \hfill \$25,000

\medskip
\section{\bf TALKS \& SEMINARS}
{\em Key:}
{\bf S} $\equiv$ Seminar $\approx60$m;
{\bf IT} $\equiv$ Invited Talk $\approx30$m;
{\bf CT} $\equiv$ Contributed Talk $\approx20$m; 
{\bf P} $\equiv$ Poster % $>45$m

\underline{Two-stage design for failure probability estimation with Gaussian process surrogates}\\
\begin{tabular}{lrl}
IT\quad\quad & June 2025 & {\bf Spring Research Conference}, New York, NY \\
S\quad\quad & May 2025 & {\bf IMSI Workshop on UQ and ML for Complex Physical Systems}, Chicago, IL \\
S\quad\quad & Feb 2025 & {\bf IMSI Workshop on UQ for Digital Twins}, Chicago, IL \\
S\quad\quad & Feb 2025 & {\bf Insper (S\~ao Paulo, Brazil)}, virtual \\
CT\quad\quad & Oct 2024 & {\bf Adv. in Interdisciplinary Statistics and Combinatorics}, Greensboro, NC \\
\end{tabular}

\underline{Contour location using deep Gaussian processes}\\
\begin{tabular}{lrl}
S\quad\quad & Nov 2024 & {\bf Chemical and Process Industries Division Webinar}, virtual \\
IT\quad\quad & May 2024 & {\bf Design and Analysis of Experiments Conference}, Blacksburg, VA \\
S\quad\quad & Mar 2024 & {\bf Arizona State University Fireside Chat}, virtual \\
CT\quad\quad & Jan 2024 & {\bf AIAA Scitech Forum}, Orlando, FL \\
IT\quad\quad & Oct 2023 & {\bf Fall Technical Conference}, Raleigh, NC \\
S\quad\quad & Sep 2023 & {\bf Duke University}, Durham, NC \\ 
S\quad\quad & July 2023 & {\bf NASA NSET Meeting}, virtual \\
\end{tabular}

\underline{Deep Gaussian process surrogates}\\
\begin{tabular}{lrl}
S\quad\quad & Mar 2025 & {\bf Virginia Tech National Security Institute}, Blacksburg, VA \\
IT\quad\quad & July 2024 & {\bf ISBA World Meeting}, Venice, Italy \\
S\quad\quad & Mar 2024 & {\bf ASA Section on Defense and National Security Webinar}, virtual \\
CT\quad\quad & Feb 2024 & {\bf SIAM Conference on UQ}, Trieste, Italy \\
S\quad\quad & Jan 2023 & {\bf Baylor University}, Waco, TX \\
S\quad\quad & Jan 2023 & {\bf North Carolina State University}, Raleigh, NC \\
S\quad\quad & Jan 2023 & {\bf University of Virginia}, Charlottesville, VA \\
S\quad\quad & Dec 2022 & {\bf National Institute of Standards and Technology}, Gaithersburg, MD \\
S\quad\quad & Dec 2022 & {\bf University of Florida}, Gainesville, FL \\
S\quad\quad & Nov 2022 & {\bf The Ohio State University}, Columbus, OH \\
S\quad\quad & Nov 2022 & {\bf University of South Carolina}, Columbia, SC \\
\end{tabular}

\pagebreak
\section{}
\hfill {\bf Curriculum Vitae:} Annie S. Booth \  --- \  4
\medskip

\underline{Vecchia-approximated deep Gaussian processes for computer experiments}\\
\begin{tabular}{lrl}
IT & Aug 2024 & {\bf Joint Statistical Meetings}, Portland, OR \\
IT & May 2023 & {\bf Spring Research Conference}, Banff, Alberta, Canada \\
IT & Aug 2022 & {\bf Joint Statistical Meetings}, Washington, D.C. \\
IT & Jun 2022 & {\bf Quality and Productivity Research Conference}, virtual \\
CT & Apr 2022 & {\bf SIAM Conference on Uncertainty Quantification}, virtual \\
CT & May 2022 & {\bf Spring Research Conference}, virtual \\
\end{tabular}

\underline{Active learning for deep Gaussian process surrogates}\\
\begin{tabular}{lrl}
IT & Oct 2022 & {\bf Fall Technical Conference}, Park City, UT \\
CT & Oct 2022 & {\bf Adv. in Interdisciplinary Statistics and Combinatorics}, Greensboro, NC \\
P & Oct 2022 & {\bf Virginia Tech Corporate Partners Conference}, Blacksburg, VA \\
P & Aug 2022 & {\bf IMSI Workshop on Gaussian Processes}, Chicago, IL \\
CT & Feb 2022 & {\bf SIAM Conference on Parallel Processing for Scientific Computing}, virtual \\
CT & Oct 2021 & {\bf Virginia Tech Corporate Partners Conference}, Blacksburg, VA \\
CT & Oct 2021 & {\bf INFORMS Annual Meeting}, virtual \\
S & Oct 2021 & {\bf Virginia Tech Deptartment of Statistics Colloquium}, virtual \\
IT & Aug 2021 & {\bf Joint Statistical Meetings}, virtual \\
CT& Jul 2021 & {\bf ISBA World Meeting}, virtual \\
S & Mar 2021 & {\bf Virginia State University}, virtual \\
CT & Oct 2020 & {\bf Virginia Tech Corporate Partners Conference}, virtual \\
\end{tabular}

\medskip
\section{OTHER \\ EMPLOYMENT}

{\sc NASA Langley Research Center}: graduate research assistant; May - December 2021

{\sc Eastman Chemical Company}: applied statistics intern; May - August 2019

\medskip
\section{OTHER \\ RESEARCH \\EXPERIENCE}

{\sc Virginia Tech Softball}: senior analyst.  Applying Markov chain theory and Monte Carlo simulation to advise coaching decisions; 2019 - 2020

{\sc Virginia Tech Statistical Applications and Innovations Group}: lead consultant.  Providing statistical consulting to graduate students and faculty; 2019 - 2020


\medskip
\section{LECTURING}

{\sc ST 370 Probability and Statistics for Engineers, NC State University}: undergraduate calculus-based introductory statistics course covering probability, estimation, hypothesis testing, regression, and analysis of variance with applications various engineering fields. Bi-weekly 75-minute lectures; Fall 2023 \& Fall 2024.

{\sc STAT 4714 Probability and Statistics for Electrical Engineers, Virginia Tech}: undergraduate introductory statistics course covering probability, random varialbes, estimation, hypothesis testing, regression, and analysis of variance with applications in electrical engineering. Six-week online course; Summer 2023. Tri-weekly 50 minute lectures; Spring 2025.

{\sc STAT 3615 Biological Statistics, Virginia Tech}: undergraduate introductory statistics course covering descriptive and inferential statistics with applications to biological sciences. Bi-weekly 75-minute lectures; Fall 2019 \& Fall 2022.


%\medskip
%\section{OTHER TEACHING EXPERIENCE}
%{\sc STAT 2004 Introductory Statistics, Virginia Tech}: introductory statistics course for non-STEM majors.  Teaching Assistant and Recitation Leader under Hamdy Mahmoud; Fall 2018 \& Spring 2019.
%{\sc STAT 3615 Biological Statistics, Virginia Tech}: undergraduate introductory statistics course.  Teaching Assistant under Frances McCarty; Fall 2018.
%{\sc Virginia Tech Statistical Applications and Innovations Group Short Courses}: instructing single-day courses in statistical methods and programming; 2019 - 2020.

\pagebreak
\section{}
\hfill {\bf Curriculum Vitae:} Annie S. Booth \  --- \  5
\medskip
\section{\bf SERVICE}

Fall Technical Conference Chair; 2026 \\
ASA Section on Physical and Engineering Sciences Council of Sections Representative; 2025 \\
Two-time panelist for NSF Division of Mathematical Sciences; 2024 and 2025 \\
CPID Fall Technical Conference Program Representative; 2024 - 2025 \\
Associate Editor, {\it Technometrics}; 2023 - Present \\
Virginia Tech Corporate Partners Committee; 2019-2021 \\
Mu Sigma Rho, Vice President of Virginia Tech Chapter; 2020-2022

\medskip
\section{\bf PROFESSIONAL MEMBERSHIP}

American Statistical Association, Section on Physical and Engineering Sciences; 2021 - Present \\
International Society for Bayesian Analysis; 2021 - Present \\

\end{resume}
\end{document}
